---
title: "Read Me!"
author: "Kammler Niclas"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Readme Document for Master Thesis 

This document is an equivalent to the readme document from github. Here, I will explain the Naming of the Variables, define the packages that have to be loaded and explain the data processing precedure used to create a language based recommender system for a craftbeer online shop. 

# Abreveations: 
* Biertraum: Bt
* RateBeer: Rb 
* Bierothek:Bk
* Untappt: Ut
* User: U
* Rating: R
* Item: I 
* Comments: C
* Reviews: Rev
* Matrix: m 
* Data Frame: df

# Naming
 * **Datasets, dataframes and tables** must be named after the following patter: Origin_Content  E.g. "Bt_Survey"; "Rb_U_R"; "Ut_U_I_Rev"
 * Names always indicate the used Columns (except for indizes)
 * temporarily used data must be named: content.type_temp E.g. "residual.plot_temp"
 * arrays must be named: 
 * Variables must be named: type_var E.g. iterations_var
 
 After executing the Functions data.PreStep and Visulisation you will receive the following result: 
 
 
 
 To be able to run the code, make sure to load the following functions: 
```{r error=FALSE}
###########
set.seed(420)


sampling <- function(.data, siZe){
  sampled_data <- .data %>% 
    splitstackshape::stratified(.data, group = style,  
                                size = siZe, 
                                keep.rowids = FALSE) %>%
    drop_na() 
  return(sampled_data)}

beer_proc_meta <- function(beers){ #this function prepares the beer documents
  beers <<- beers %>% rename(beer_id = id)
 
  beers_meta <- beers%>%
    dplyr::select(-notes) %>% 
    filter_at(.vars = c("beer_id", "style", "abv"), any_vars(!is.na(.))) %>% #removeobservations with missing values
    mutate_if(is.character, as.factor) %>% #convert characters to factors
    filter(!retired)  %>% 
    group_by(style) %>% 
    mutate(style_mean.abv = mean(abv, na.rm = TRUE)) %>%  
    ungroup()%>% 
    group_by(beer_id) %>% 
    mutate(item_diff.abv = (abv - style_mean.abv)) %>% #calculates the difference of ABV in beer to style-mean
    ungroup() 
  return(beers_meta)
} 

beers_proc_text <-function(beers){ 
  beer_docs <- beers%>% 
    rename(beer_id = id) %>% 
    dplyr::select(beer_id, notes) %>% 
    mutate(description = ifelse(notes != "No notes at this time.", TRUE, FALSE))
  
  return(beer_docs)
  }

FUN_cut_reviews <- function(reviews, beers_filtered) {
  cut_reviews <- reviews %>% 
    mutate(user = paste("u", as.numeric(factor(reviews$username)), sep = "")) %>%
    dplyr::filter(!is.na(overall)) %>% 
    dplyr::filter(beer_id %in% beers_meta$beer_id) %>% #we make sure to only retain ratings for beers, contained in the beers_meta set
      mutate(doc_id = paste0(date, '_', beer_id, '_', user)) 
    
  return(cut_reviews)}

FUN_reviews_meta <- function(cut_reviews){
  reviews_meta <- cut_reviews %>% 
    dplyr::select(-c(text, overall, look, smell, taste, feel)) %>% 
    arrange(user, date) %>%
    group_by(user) %>%
    mutate(month = lubridate::month(date),
           IPT = as.numeric(difftime(date, lag(date), units = "days")),
           mean_IPT = mean(IPT, na.rm = TRUE),
           IPT = ifelse(row_number() == 1, mean_IPT, IPT),
           season = case_when(
             month %in% c(3, 4, 5) ~ "Spring",
             month %in% c(6, 7, 8) ~ "Summer",
             month %in% c(9, 10, 11) ~ "Fall",
             month %in% c(12, 1, 2) ~ "Winter",
             TRUE ~ NA_character_)) %>%
    ungroup()%>%
    left_join(beers_meta[, -c( 7, 9, 10, 11)], by = "beer_id") 
  reviews_meta$season <- as.factor(reviews_meta$season)
  reviews_meta <- reviews_meta[,-c(2, 6)]
  reviews_meta$doc_id = cut_reviews$doc_id
  return(reviews_meta)
  }


rating_data_processing <- function(cut_reviews, target) {
  rating_data <- cut_reviews %>%
    dplyr::select(user, beer_id, !!sym(target)) %>% as.data.frame()  # Use !!sym(target) to evaluate the target variable
  
  U_I_R <- as(rating_data, "realRatingMatrix")
  
  return(U_I_R)
}


 

rev_text_data_processing <- function(cut_reviews) {
  rev_text <- cut_reviews %>%
   dplyr::select(doc_id, user, text) %>% 
    group_by(user) %>% 
    mutate(word_count = str_count(text, "\\S+")) %>% 
    ungroup()
  return(rev_text)

}

user_processing <- function(reviews_meta, rating_data, rev_text_data) { 
  # Combine the datasets to get a comprehensive dataset similar to reviews_filtered
  reviews_temp <- reviews_meta %>% dplyr::select(c(1,4,6,17,18)) %>%
    left_join(rev_text[,c("doc_id", "word_count")], by = "doc_id") %>% left_join(beers_meta[,c("beer_id", "style")], by = "beer_id")
  
  user_profiles <- reviews_temp %>%
    group_by(user) %>%
    summarise(
      nu.ratings = n(),
      VarSeekStyle = (n_distinct(style)),
      IPT_mean = mean(IPT, na.rm = TRUE),
      aff.abv = mean(item_diff.abv, na.rm = TRUE),
      mean_word_count = mean(word_count, na.rm = TRUE)
    )
  
  # Remove bots and users with fewer than 5 ratings
 
  
  
  return(user_profiles)
}

```
Furthermore, we have to set some methods:
```{r}

setAs("data.frame", "realRatingMatrix", function(from) {
  user	<- from[, 1]
  item	<- from[, 2]
  if (ncol(from) >= 3)
    rating <- as.numeric(from[, 3])
  else
    rating <- rep(1, length(item))
  
  i <- factor(user)
  j <- factor(item)
  
  dgT <-
    new(
      "dgTMatrix",
      i = as.integer(i) - 1L,
      j = as.integer(j) - 1L,
      x = rating,
      Dim = c(length(levels(i)), length(levels(j))),
      Dimnames = list(levels(i), levels(j))
    )
  
  as(dgT, "realRatingMatrix")
})


setAs("realRatingMatrix", "data.frame", function(from) {
  trip <- as(from, "dgTMatrix")
  data.frame(user = rownames(from)[trip@i + 1L],
             item = colnames(from)[trip@j + 1L],
             rating = trip@x)[order(trip@i),]
})

setMethod("getList", signature(from = "realRatingMatrix"),
          function(from,
                   decode = TRUE,
                   ratings = TRUE,
                   ...) {
            trip <- as(from, "dgTMatrix")
            
            lst <- split(trip@j , trip@i)
                                            
            
            if (decode)
              lst <- lapply(lst, function(y)
                colnames(from)[y])
            
            else
              names(lst) <- NULL
            
            if (!ratings)
              return(lst)
            
            rts <- split(trip@x, f = trip@i)
            
              
            
                                        
            for (i in 1:length(rts)) {
              names(rts[[i]]) <- lst[[i]]
              
                }
            
            rts
          })

```


 
 